### 2017-10-23 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Some text update. Need to check merge with code changes at home

        \section{Application in structural geological modeling}
        In this work, these methods of Bayesian analysis and decision theory are applied in the field of geological structural modeling. The fundamental approach follows closely the research conducted by \citet{delaVarga2016} and builds upon their findings.\\
        According to them, structural geological modeling can be regarded as a forward problem and the elements of Bayesian inference can be specified in this context as follows:
        \begin{enumerate}
        	\item \textbf{Mathematical forward model ($M$)}: The connections between parameters $\theta$ and observed data $y$ are defined in this mathematical model. ...
        	\item \textbf{Model parameters ($\theta$)}: These model-defining parameters, such as the position or dip of layers and faults in geological settings, can be deterministic or stochastic. In the latter case, they are uncertain parameters to which a probability distribution is assigned.
        	\item \textbf{Observed data ($y$)}: This is any type of additional information that can be related to the forward modeling results and might possibly be used to reduce uncertainty. Such data can be gained by measurements and observations, for example by core sampling, well-log analysis or seismic acquisition. 
        	\item \textbf{Likelihood functions ($p(y|\theta)$}: Links between the previous parameters $\theta$ and the additional data $y$ are established by these functions in way that they reflect the likelihood of the parameter states given the observations \citep{delaVarga2016}.
        \end{enumerate}

@@

			Where reservoir thickness is given by $h_{res}$, seal thickness by $h_{seal}$ and reservoir depth, which is always a negative value, by $d_{res}$.

@@

		\subsection{Implementation of reservoir-related likelihoods in the 3D model}

>>>>

        \section{Application in structural geological modeling}\label{sec:bayes_in_struc_modeling}
        In this work, these methods of Bayesian analysis and decision theory are applied in the field of geological structural modeling. The fundamental approach follows closely the research conducted by \citet{delaVarga2016} and builds upon their findings.\\
        According to them, structural geological modeling can be regarded as a forward problem and the elements of Bayesian inference can be specified in this context as follows:
        \begin{enumerate}
        	\item \textbf{Mathematical forward model ($M$)}: The connections between parameters $\theta$ and observed data $y$ are defined in this mathematical model. ...
        	\item \textbf{Model parameters ($\theta$)}: These model-defining parameters, such as the position or dip of layers and faults in geological settings, can be deterministic or stochastic. In the latter case, they are uncertain parameters to which a probability distribution is assigned.
        	\item \textbf{Observed data ($y$)}: This is any type of additional information that can be related to the forward modeling results and might possibly be used to reduce uncertainty. Such data can be gained by measurements and observations, for example by core sampling, well-log analysis or seismic acquisition. 
        	\item \textbf{Likelihood functions ($p(y|\theta)$}: Links between the previous parameters $\theta$ and the additional data $y$ are established by these functions in way that they reflect the likelihood of the parameter states given the observations \citep{delaVarga2016}.
        \end{enumerate}

@@

			Where reservoir thickness is given by $h_{res}$, seal thickness by $h_{seal}$ and reservoir depth, which is always a negative value, by $d_{res}$.
			This 1D model is then placed inside the Bayesian probabilistic modeling framework

@@

		\subsection{Implementation of reservoir-related likelihoods in the 3D model}
		As for the 1D case before, for the 3D case it is assumed that additional information is provided in the form of layers thickness likelihoods. In this geological scenario, the information might have been gained for example from additional seismic observations or from core sample data from a well nearby. Likelihoods could also be derived from knowledge of the geological history of the formation, such as the depositional environment of sedimentary layers. Assuming a possible correlation of nearby core samples with the layers in our model section, layer thickness likelihoods can be deduced respectively.\\
		First of all, a method to determine layer thicknesses in our model realizations has to be introduced. Here, as single X- and Y-point (1D column in Z) in the footwall of the model is chosen as a measure for the thickness of the layers. In this column, point coordinates for the layer interfaces had been defined in the original data frame and can be observed as they are altered in the interpolation data frame for each iteration. The column is located centrally in the overall model block, as well as the original potential trap structure (X~=~1100~m,Y~=~1000~m) and is thus presumed to be representative and of significance for the reservoir analysis. Thickness variations are traced and vary relative to the changes in the layer interface positions, given by their uncertainties in Z-values.\\
		After defining these thickness to point-positional dependencies, thickness likelihoods are implemented as probability distributions, as done for the 1D model. Various types of geological information, conclusions and expectations can be expressed by adapting mean and standard deviation of these normal distributions. For core sampling, for example, information might be evenly provided for all layers, irrespective of depth, so that similar standard distributions might be assigned to all layer thicknesses. Alternatively, taking into account certain depositional environments for which high thickness variablity is characteristic, specific standard deviations can be raised accordingly. Some representative cases are presented in Chapter \ref{cha:results}.

		\subsection{Bayesian analysis and valuation of the 3D model}
		According to the methods introduced in Sections \ref{sec:bayes} and \ref{sec:bayes_in_struc_modeling}, the 3D geological model is to be incorporated in a probabilistic modeling framework and analyzed from a Bayesian perspective.
